Normalization: A pipeline to analyse time-course gene expression data

### 2019-03-05 scripts/01_quality_control_normalization.Rmd
FIX 01_quality_control_normalization.Rmd doesn't depend on written data

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)
library(ggplot2)
library(stats)

@@

```{r}

# Now load in the metadata
meta = read.delim("data/shoemaker2015/mice_meta.tsv", sep="\t")
write.table(data, ".results/quantile_normalized.txt")
```

>>>>

```{r echo=FALSE, results="hide", message=FALSE}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)
library(ggplot2)
library(stats)

@@

```{r}
# Now load in the metadata
# meta = read.delim("data/shoemaker2015/mice_meta.tsv", sep="\t")
data(shoemaker2015)
meta = shoemaker2015$meta
write.table(data, ".results/quantile_normalized.txt")
```
